---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/musicbrainz)](http://cran.r-project.org/package=musicbrainz)


# musicbrainz

The goal of musicbrainz is to make it easy to call the MusicBrainz api from R.

## Installation

You can install musicbrainz from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikkelkrogsholm/musicbrainz")
```

## Example

This is a basic example which shows you how to solve a common problem.

Lets find the Prince of Darkness in MusicBrainz

```{r ozzy}
library(musicbrainz)

ozzy_search <- mb_search("artist", 'artist:"ozzy osbourne"')
```

We can then see Ozzys mbid 
```{r id}
ozzy_search[["artists"]][[1]][["id"]]
```

And if we have a mbid then we can call the lookup function with that id.

```{r lookup}
ozzy_lookup <- mb_lookup("artist", "8aa5b65a-5b3c-4029-92bf-47a544356934")
```
